Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-10 paper/paper.tex
pass on clusterization

\Mar{explain what is a bucket (we refer to it later).}

Figure~\ref{fig:err-messages} shows the error messages produced by a
\lo warning. Note that all message appear to be related to the same
problem.

%% \begin{figure}[h]
%% \begin{tabular}{ll}
%% \veight{} & ``Unexpected end of input''\\
%% \jsc{} & ``Unexpected end of script''\\
%% \smonkey{} & ``Expected expression, got end of script''
%% \end{tabular}
%% \caption{\label{fig:err-messages}Example error messages associated
%%   with a \lo{} warning. In this case, the test passes in \chakra.}
%% \end{figure}

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}True positive example of LO
    warnings.}
\end{figure}

>>>>

Clusterization helps to group tests that fail for similar reasons. We
only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
that arise from the test case, which are typically
distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
error messages produced by a ``\lo'' warning. Any warning, including
this one, that has this same message signature will be included in the
same cluster, which we may also refer as a ``bucket''.

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}True positive example of a ``\lo''
    warning.}
\end{figure}
